---
title: "Marketing recommendations for Financial Management Company to sell retirement income products "
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
  html_document:
    df_print: paged
---

```{r include=FALSE}
# Course: BUAN 5210
# Purpose: Illustrate flexdashboard mechanics
# Author: Ying Xue
# Date: Mar 21, 2019

```

```{r}
# library package
library(flexdashboard)
library(ggplot2)
library(plotly)
# Load saved image of the office Tech Appendix workspace
load("Final_TA.RData")
```




Column {data-width=375}
-----------------------------------------------------------------------

### How participation of the retirement plan related to value of Financial Security? {data-height=700}

```{r echo = FALSE, include = TRUE}
# Show the plot that was made in the Technical Appendix and saved in the workspace 
ggplotly(g1)

```

### How participation of the retirement plan related to age? {data-height=700}

```{r echo = FALSE, include = TRUE}
# Show the plot that was made in the Technical Appendix and saved in the workspace 
ggplotly(g3)

```



Column {data-width=400}
-----------------------------------------------------------------------

### How Value of Financial Security differentiated by age? {data-height=700}
```{r echo = FALSE, include = TRUE}
# Show the plot that was made in the Technical Appendix and saved in the workspace 
ggplotly(g5)

```

### How Value of Financial Security differentiated by marital status?{data-height=400}

```{r echo = FALSE, include = TRUE}
# Show the plot that was made in the Technical Appendix and saved in the workspace 
ggplotly(g8)

```


Column {data-width=375}
-----------------------------------------------------------------------


### How participation of the retirement plan related to both the Householdincome and marital status?{data-height=400}
```{r echo = FALSE, include = TRUE}
# Show the plot that was made in the Technical Appendix and saved in the workspace 
ggplotly(g6)

```

### Contact Information {data-height=100}
  
If you have any question, feel free to contact me [Ying Xue](www.linkedin.com/in/ying-xue-2019/)

