---
title: "BUAN5310 group project"
output:
  html_document:
    df_print: paged
---
```{r echo = FALSE, warning = FALSE, message = FALSE}
# Course: BUAN5310
# Title: Modeling Passengers’ Airport and Airline Choice Behavior
# Purpose: EDA and variable pre-selection
# Date: June 8th, 2019
# Author: Yifan Xiang, 

```

```{r echo = FALSE, warning = FALSE, message = FALSE}

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)

```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Load packages
library(tidyverse)
library(gridExtra)
library(GGally)
library(stringr)
library(janitor)
library(grid)
library(readxl)
library(gdata)
library(MASS)
```

# Load, review and modify data

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Load datasets
choice<- read_excel("airport_choice_survey_EN_ver2.0_Capstone.xlsx", sheet = "Data", na = "NA")

# remove ID, FlightNo, DepartureHr, DepartureMn  
data<- dplyr::select(choice, -c(ID,FlightNo,DepartureHr,DepartureMn))

# Review Data
summary(data)
```


```{r echo = FALSE, warning = FALSE, message = FALSE}

# Remove records with NA in Airport and Airline columns
data <- data %>%
  filter(!is.na(Airport)) %>%
  filter(!is.na(Airline))

## 3 NA in Gender, 2 NA in Destination, 4 NA in SeatClass, 150 NA in Airfare, 194 NA in AccessCost, 94 NA in AccessTime, 127 NA in Income, 388 NA in Mileage

# Rename some variables for easier analysis
data <- data %>% 
 mutate(Airport = ifelse(Airport == 1, "ICN", "GMP")) %>%
  mutate(Airline = ifelse(Airline == 1, "Korean Air", 
                   ifelse(Airline == 2, "Asiana Airlines", 
                   ifelse(Airline == 3,"Korean LLC", "Foreign Carriers")))) %>%

  mutate(Nationality  = ifelse(Nationality == 1, "Korea",
                       ifelse(Nationality == 2, "China",
                       ifelse(Nationality == 3, "Japan",
                       ifelse(Nationality == 4, "Southeast Asia", "Other"))))) %>%
  
  mutate(TripPurpose = ifelse(TripPurpose == 1, "Leisure",
                        ifelse(TripPurpose == 2, "Business", "Other"))) %>%
 
   mutate(ProvinceResidence = ifelse(ProvinceResidence == 1,"Seoul",
                    ifelse(ProvinceResidence == 3, "Kyungki-do","Other"))) %>%

    mutate(GroupTravel = ifelse(GroupTravel == 1,"Yes", "No")) %>%
  
# regroup Frequent Flight Destination column: 4,5,6,7 become other
   mutate(FrequentFlightDestination = ifelse(FrequentFlightDestination == 1, "Southeast Asia", 
                                     ifelse(FrequentFlightDestination == 2,"China",
                                     ifelse(FrequentFlightDestination == 3, "Japan","Other")))) %>%
  
  mutate(Destination = ifelse(Destination ==1, "China",
                       ifelse(Destination ==2, "Japan",
                       ifelse(Destination ==3, "SouthEast Asia", "Other")))) %>%
  
  mutate(DepartureTime = ifelse(DepartureTime == 1, "6am-12pm",
                         ifelse(DepartureTime ==2, "12pm-6pm",
                         ifelse(DepartureTime ==3, "6pm-9pm","9pm-6am")))) %>%

# NA in seat class is categorize as economy
  mutate(SeatClass = ifelse(SeatClass == 3 | SeatClass == 2, "First/Business", "Economy")) %>% 
  
  mutate(Gender = ifelse(Gender == 1, "Male", 
               ifelse(Gender == 2, "Female", NA))) %>% 
  
  mutate(ModeTransport = ifelse(ModeTransport == 1, "Car",
                         ifelse(ModeTransport == 2, "Taxi",
                         ifelse(ModeTransport == 6, "Limo",
                         ifelse(ModeTransport < 9, "Transit", "Other"))))) %>% 
  
  mutate(Occupation = ifelse(Occupation == 2 | Occupation == 3 | Occupation == 5 | Occupation == 7, "Professional", 
                      ifelse(Occupation == 8, "Student",
                      ifelse(Occupation == 9, "Housewife",
                      ifelse(Occupation == 10 | Occupation == 11, "None", "Other"))))) 

# Drop Mileage, Mileage Airline column due to too many missing values
data <- dplyr::select(data, -c(Mileage, MileageAirline))

summary(data)

```

Now, we deal with missing values. For numeric variables, we take averages to fill in the missing values. Categorical variables are done on a case-by-case basis, NA values typically lumped in with "Other".

```{r echo = FALSE, warning = FALSE, message = FALSE}
# fix NAs in data

# Put in more specific averages for missing Airfare data
avg <- median(data$Airfare, na.rm = TRUE)
avgs <- data %>% 
  group_by(Airport, Airline, Destination) %>% 
  summarise(median_airfare = median(Airfare, na.rm = TRUE)) %>% 
  filter(median_airfare != "NaN") %>% 
  filter(!is.na(Destination))
data <- left_join(data, avgs, by = c("Airport", "Airline", "Destination"))
data$Airfare <- ifelse(is.na(data$Airfare), data$median_airfare, data$Airfare)
data$Airfare <- ifelse(is.na(data$Airfare), avg, data$Airfare)
data <- dplyr::select(data, -median_airfare)

# put in specific averages for AccessCost and AccessTime
avgs <- data %>% 
  group_by(Airport,ProvinceResidence) %>% 
  summarise(median_accesscost = median(AccessCost, na.rm = TRUE),
            median_accesstime = median(AccessTime, na.rm = TRUE))
data <- left_join(data, avgs, by = c("Airport", "ProvinceResidence"))
data$AccessCost <- ifelse(is.na(data$AccessCost), data$median_accesscost, data$AccessCost)
data$AccessTime <- ifelse(is.na(data$AccessTime), data$median_accesstime, data$AccessTime)
data <- dplyr::select(data, -c("median_accesscost", "median_accesstime"))

# Put in specific averages for Income
avg <- median(data$Income, na.rm = TRUE)
data <- data %>% 
  mutate(age_group = ifelse(Age < 18, "child", 
                     ifelse(Age < 30 & Age >=18, "18-30",
                     ifelse(Age < 50 & Age >= 30, "30-49",
                     ifelse(Age < 70 & Age >= 50, "50-69", "70+")))))
avgs <- data %>% 
  group_by(age_group, Occupation) %>% 
  summarise(median_income = median(Income, na.rm = TRUE))
data <- left_join(data, avgs, by = c("age_group", "Occupation"))
data$Income = ifelse(is.na(data$Income), data$median_income, data$Income)
data$Income = ifelse(is.na(data$Income), avg, data$Income)
data <- dplyr::select(data, -c("age_group", "median_income"))

# Destination labelled other
data$Destination <- ifelse(is.na(data$Destination), "Other", data$Destination)

# Seatclass as economy
data$SeatClass <- ifelse(is.na(data$SeatClass), "Economy", data$SeatClass)

# Gender as female (only 3 cases)
data$Gender <- ifelse(is.na(data$Gender), "Female", data$Gender)

# Change Income from numerical to character
data$Income <- as.character(data$Income)


```

```{r}
summary(data)
str(data)
```


# Basic Visualization

## Univariate Data Exploration

### categorical variables

We dealt with outliers by grouping them into larger groups

```{r echo = FALSE, warning = FALSE, message = FALSE}
  

grid.arrange(
  data %>% 
    ggplot(aes(Airport)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(Airline)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(GroupTravel)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(ModeTransport)) +
    geom_bar() +
    coord_flip(),
  data %>% 
    ggplot(aes(Occupation)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(Nationality)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(TripPurpose)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(ProvinceResidence)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(FrequentFlightDestination)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(Destination)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(SeatClass)) +
    geom_bar() + 
    coord_flip(),
  data %>% 
    ggplot(aes(Gender)) +
    geom_bar() + 
    coord_flip(),
   data %>% 
    ggplot(aes(DepartureTime)) +
    geom_bar() + 
    coord_flip(),
   data %>%
    ggplot(aes(Income)) +
    geom_bar()+
    coord_flip(),
  ncol = 4
  )

```


### numerical variables

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Cap values to reduce the impact of outliers
data <- data %>% 
  mutate(TripDuration = ifelse(TripDuration > 300, 300, TripDuration)) %>% 
  mutate(FlyingCompanion = ifelse(FlyingCompanion > 15, 15, FlyingCompanion)) %>% 
  mutate(NoTripsLastYear = ifelse(NoTripsLastYear > 20, 20, NoTripsLastYear)) %>% 
  mutate(Airfare = ifelse(Airfare > 200, 200, Airfare)) %>% 
  mutate(AccessCost = ifelse(AccessCost > 40000, 40000, AccessCost)) %>% 
  mutate(AccessTime = ifelse(AccessTime > 200, 200, AccessTime))

# Count histogram
count_hist <- function(x){
  x + geom_histogram(bins = 52) +
    theme_bw() +
    theme(panel.border =  element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    labs(y = "Count")
}

# Create bar graphs
grid.arrange(
  count_hist(ggplot(data, aes(Age))),
  count_hist(ggplot(data, aes(TripDuration))),
  count_hist(ggplot(data, aes(FlyingCompanion))),
  count_hist(ggplot(data, aes(NoTripsLastYear))),
  count_hist(ggplot(data, aes(Airfare))),
  count_hist(ggplot(data, aes(NoTransport))),
  count_hist(ggplot(data, aes(AccessCost))),
  count_hist(ggplot(data, aes(AccessTime)))
)

```

# Variable Selection

We used a combination of Anova and Chi-Squared tests, and Stepwise method to determine which variables to include in our model. We elected to include only variables with p<0.05 and selected by Stepwise method in our model.

```{r echo = FALSE, warning = FALSE, message = FALSE}
# turn character vectors into factors
data <- data %>% mutate_if(is.character, as.factor)

# create a data frame of categorical and of numeric variables
is.fact <- sapply(data, is.factor)
data_factors <- data[, is.fact]
data_notfactors <- data[, !is.fact]

# summary of final data
print(summary(data))
```


## Airport variables selection

### Anova test & Chi-Squared test
```{r echo = FALSE, warning = FALSE, message = FALSE}

# Only select variables with P-value less than 0.05
print("Variables to include in the Airport Model:")

#Chi-Squared test for Airport
for (var in names(data_factors)){
  tab <- table(data$Airport, data[[var]])
  pval <- chisq.test(tab, simulate.p.value = TRUE)$p.value
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}
#Anova test for Airport
for (var in names(data_notfactors)) {
  anova = aov(data[[var]]~data$Airport)
  pval <- unlist(summary(anova))["Pr(>F)1"]
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}
```

From our Chi-Squared and Anova tests, we have informed the initial variables we expect to include in our models (12 variables selected). 

### Stepwise

We use stepwise function to rechoose variables and compare the result we got from Anova and Chi-Squared tests.

```{r echo = FALSE, warning = FALSE, message = FALSE}

## Airport full model
full.model.airport <- glm(Airport~., data = data, family = binomial)
summary(full.model.airport)
```

Variables that are significant at 5% level: Airline, Nationality, FlyingCompanion, FrequentFlightDestination, Destination, DepartureTime, NoTransport, ModeTransport, AccessCost, and Income.

```{r}
# Airport backward selection
backward_airport <- stepAIC(full.model.airport, direction = "backward", trace = FALSE)
summary(backward_airport)
```

AIC dropped from 325.94 to 311.54.
Variables that are selected by the backward method: Airline, Nationality, FlyingCompanion, FrequentFlightDestination, Destination, DepartureTime, NoTransport, ModeTransport, AccessCost, and Ocupation.


```{r}
# Airport forward selection
nothing.airport <- glm(Airport~1,  data = data,family = binomial)
forwards.airport <- step(nothing.airport, scope = list(lower = formula(nothing.airport), upper = formula(full.model.airport)), direction = "forward", trace = FALSE) 
summary(forwards.airport)
```

Forwards method provides the same result as backwards method.
The result we got from stepwise method is in consistent with the significant level in full model.
However, the stepwise method provides a result that is different from anova test and chi-squred test.


```{r}
# Test the logit model of the anova test result

logit_anova.airport <- glm(formula = Airport ~ Airline + Nationality + TripPurpose + FrequentFlightDestination + ProvinceResidence + Destination + DepartureTime + Occupation + Income + Age + Airfare + NoTransport, family = binomial, data = data)
summary(logit_anova.airport)
```

The AIC of logic model with variables chosen from stepwise method is lower than the AIC of logic model with variables chosen from anova test. Thus, we use variables chose from stepwise method as our starting point. 



## Multi-variate Data Exploration 

Visualize those variables to support our variable selection.

### Correlation

### categorical variables 

```{r}
# Function for heatmap
 heat_map <- function (x, y,y_title,x_title){
   x<-enquo(x)
   y<-enquo(y)
   
   
   data %>%
     group_by(!!x,!!y) %>%
     summarise(count = n())  %>%
     ggplot(aes(!!x,!!y)) +
     geom_tile(aes(fill = -count))+
     ylab(y_title) + xlab(x_title)+
     scale_fill_continuous(guide = guide_legend(title = "Count"))
      }
# Create heatmap to see relationship between Airport and selected categorical variables
grid.arrange(
  heat_map(Airport, Airline, "Airline","Airport"),
  heat_map(Airport, FrequentFlightDestination, "FrequentFlightDestination","Airport"),
  heat_map(Airport, Destination, "Destination","Airport"),
  heat_map(Airport, DepartureTime,"DepartureTime","Airport"),
  heat_map(Airport, Occupation, "Occupation","Airport"),
  heat_map(Airport, Nationality, "Nationality","Airport"),
  heat_map(Airport, ModeTransport, "ModeTransport", "Airport"), 
  heat_map(Airport, ProvinceResidence, "ProvinceResidence", "Airport"),
  heat_map(Airport, Income, "Income", "Airport")
  
)
```

ProvinceResidence is very similar to Nationality, according to the heat_map, we choose Nationality, drop ProvinceResidence
Income is very similar to Occupation, according to the heat_map, we choose Occupation, drop Income

### numerical variables 

```{r}
# Create box-plot for numerical variables
grid.arrange(
ggplot(data, aes(Airport, Age)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airport, AccessCost)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airport, Airfare)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airport, NoTransport)) +
  geom_boxplot() +
  coord_flip(),
ncol = 3

)

```

According to the box-plot, we drop NoTransport.
Since AccessCost is already reflected ModeTransport, we drop ModeTransport
Since Age is already reflected in Occupation, we drop Age
Since AccessCost is already reflected in NoTransport, and NoTransport is more Significant than AccessCost, we keep NoTransport

*** Summary ***
Variables chose for Airport selection model:
 Airline, FrequentFlightDestination, Destination, DepartureTime, Occupation,  Nationality, AccessCost, Airfare
 
```{r}
# Logit model - add interaction term: Airfare * Destination

logit.final.airport <- glm(Airport ~ Airline + FrequentFlightDestination + Destination+DepartureTime + Occupation + Nationality + NoTransport + Airfare + Airfare * Destination, family = binomial, data = data)
summary(logit.final.airport)
```

### Airline variables selection

### Anova test & Chi-Squared test
```{r echo = FALSE, warning = FALSE, message = FALSE}
#Chi-Squared test for Airline

print("Variables to include for the Airline Models:")
for (var in names(data_factors)){
  tab <- table(data$Airline, data[[var]])
  pval <- chisq.test(tab, simulate.p.value = TRUE)$p.value
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}
#Anova test for Airport
for (var in names(data_notfactors)) {
  anova = aov(data[[var]]~data$Airline)
  pval <- unlist(summary(anova))["Pr(>F)1"]
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}


```
From our Chi-Squared and Anova tests, we have informed the initial variables we expect to include in our models (14 variables selected). 

### Stepwise

```{r echo = FALSE, warning = FALSE, message = FALSE}
## airline
library(nnet)
full.model.airline <- multinom(Airline~., data = data)
summary(full.model.airline)


```

```{r echo = FALSE, warning = FALSE, message = FALSE}

# Backward method
backward_airline <- stepAIC(full.model.airline, direction = "backward", trace = FALSE)
summary(backward_airline)
```

AIC dropped from 1110.524 to 1070.103
Variables that are selected by the backward method: Airport, TripDuration, FlyingCompanion, FrequentFlightDestination, Destination,DepartureTime, SeatClass, Airfare, NoTransport, Occupation, Income


```{r}

# Forward method
nothing <- multinom(Airline~1,  data = data)

forwards_airline <- step(nothing, scope = list(lower = formula(nothing), upper = formula(full.model.airline)), direction = "forward") 
summary(forwards_airline)
```

Forward method provides the lowest AIC.
variables selcet:
Destination, Airfare, DepartureTime, Airport, FlyingCompanion, NoTransport, FrequentFlightDestination, TripDuration, NoTripsLastYear

```{r}
# Test the logit model of the anova test result
logit.anova.airline <- multinom(formula = Airline ~ Nationality + TripPurpose + ProvinceResidence + GroupTravel + FrequentFlightDestination + Destination + DepartureTime + Occupation + Age + TripDuration + FlyingCompanion + Airfare + NoTripsLastYear, data = data)
summary(logit.anova.airline)
```
The logit model of anova method provides the highest AIC, we choose to use the result from forward method as our starting point.

Variables different from Anova test and Stepwise method: 
Nationality, ProvinceResidence, GroupTravel, Occuaption, Age, 

## Multi-variate Data Exploration 

Visualize those variables to support our variable selection.

### Correlation

### categorical variables 

```{r}

# Create heatmap to see relationship between Airport and selected categorical variables
grid.arrange(
  heat_map(Airline, Airport, "Airline","Airline"),
  heat_map(Airline, FrequentFlightDestination, "FrequentFlightDestination","Airline"),
  heat_map(Airline, Destination, "Destination","Airline"),
  heat_map(Airline, DepartureTime,"DepartureTime","Airline"),
  heat_map(Airline, Occupation, "Occupation","Airline"),
  heat_map(Airline, Nationality, "Nationality","Airline"),
  heat_map(Airline, ProvinceResidence, "ProvinceResidence", "Airline")
  
)
```

According to the heatmap, we choose to drop Nationality. 

### numerical variables 

```{r}
# Create box-plot for numerical variables
grid.arrange(
ggplot(data, aes(Airline, Age)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airline, TripDuration)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airline, FlyingCompanion)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airline, NoTripsLastYear)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airline, Airfare)) +
  geom_boxplot() +
  coord_flip(),
ggplot(data, aes(Airline, NoTransport)) +
  geom_boxplot() +
  coord_flip(),
ncol = 3

)

```

According to the Box-Plot, we choose to drop NoTransport.

```{r}
logit.final.airline <- multinom(formula = Airline ~ Destination + Airfare + DepartureTime + 
    Airport + FlyingCompanion + FrequentFlightDestination + 
    TripDuration + NoTripsLastYear, data = data)

summary(logit.final.airline)
```


```{r}
# add interaction term into the model
logit.final.interaction.airline <- multinom(formula = Airline ~ Destination + Airfare + DepartureTime + 
    Airport + FlyingCompanion + FrequentFlightDestination + TripDuration + 
    NoTripsLastYear + Airfare * Destination, data = data)

summary(logit.final.interaction.airline )
```

The logit model with interaction term provides the lowest AIC.

## Try to change the levels of airline (Korean Air vs Foreign Air)


```{r}
data1 <- data %>% 
  mutate(Airline = ifelse(Airline == "Korean Air", "Korean Air",
                    ifelse(Airline == "Korean LLC", "Korean Air",
                    ifelse(Airline == "Asiana Airlines","Korean Air",
                                        "Foreign Air"))))

print(str(data1))
print(summary(data1))
```

## ANOVA & Chi-Square
```{r echo = FALSE, warning = FALSE, message = FALSE}
# turn character vectors into factors
data1 <- data1 %>% mutate_if(is.character, as.factor)

# create a data frame of categorical and of numeric variables
is.fact <- sapply(data1, is.factor)
data1_factors <- data1[, is.fact]
data1_notfactors <- data1[, !is.fact]




print("Variables to include in the Airline Model:")

#Chi-Squared test for Airport
for (var in names(data1_factors)){
  tab <- table(data1$Airline, data1[[var]])
  pval <- chisq.test(tab, simulate.p.value = TRUE)$p.value
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}
#Anova test for Airport
for (var in names(data1_notfactors)) {
  anova = aov(data1[[var]]~data1$Airline)
  pval <- unlist(summary(anova))["Pr(>F)1"]
  if(as.numeric(pval) < 0.05){
    print(var)
  }
}
```

## stepwise
```{r echo = FALSE, warning = FALSE, message = FALSE}
library(MASS)
## full model airline
full.model.airline1 <- glm(Airline~., data = data1, family = binomial)
print(summary(full.model.airline1))
```


```{r}
# Backward method
backward_airline1 <- stepAIC(full.model.airline1, direction = "backward", trace = FALSE)
summary(backward_airline1)
```


```{r echo = FALSE, warning = FALSE, message = FALSE}

# Forwards method
nothing <- glm(Airline~1,  data = data1,family = binomial)
forwards <- step(nothing, scope = list(lower = formula(nothing), upper = formula(full.model.airline1)), direction = "forward", trace = FALSE) 
summary(forwards)

```

```{r}
#test the logic model of the anova test result

model_anova <- glm(formula = Airline ~ Airport + Nationality+
                     FrequentFlightDestination+Destination+FlyingCompanion, family = binomial, data = data1)
summary(model_anova)
```

```{r}
# Add interaction term (airfare, destination) into model
model2 <- glm(formula = Airline ~ Airport + Nationality+
                     FrequentFlightDestination+Destination+FlyingCompanion + Airfare * Destination, family = binomial, data = data1)
summary(model2)
```


```{r}

# Add airfare into model
model <- glm(formula = Airline ~ Airport + Nationality+
                     FrequentFlightDestination+Destination+FlyingCompanion+Airfare , family = binomial, data = data1)
summary(model)
```

```{r}
Airline2_stepwise <- data1 %>% dplyr::select(c(Airline, Airport, FlyingCompanion, Destination, DepartureTime, SeatClass, Airfare, NoTransport, ModeTransport, AccessCost, Occupation))

Airline2_dk <- data1 %>% dplyr::select(c(Airline, Airport, Destination,Airfare))

write_csv(Airline2_stepwise,"Airline2_stepwise.csv")
write_csv(Airline2_dk,"Airline2_dk.csv")
```



# Write to CSV file

```{r}

# write airort csv file
write_csv(data, "full.csv")

```






